### 2020-10-25 Thesis-Chapter1-Introduction.tex
Termify argument maps and remove strategy notes

This thesis aims to clarify the arguments composing debate and the nature of the technical problem. After reproducing a
brief U.S.--focused history of encryption regulation, technology, and conflict, I introduce argument maps and threat
models using data flow diagrams. In the following chapters, I analyze exceptional access arguments in detail and create
a multi-level threat model, broken down by the significantly different challenges posed by \acl{DAR} and \acl{DIM}. The
thesis concludes with a set of policies and principles to apply to the problem in light of valid arguments and threats.

>>>>

This thesis aims to clarify the arguments composing debate and the nature of the technical problem. After reproducing a
brief U.S.--focused history of encryption regulation, technology, and conflict, I introduce \acp{argmap} and threat
models using data flow diagrams. In the following chapters, I analyze strategies for tacking \acp{wicked-prob}, map the
\acl{EA} arguments in detail, and create a multi-level threat model, broken down by the significantly different
challenges posed by \acl{DAR} and \acl{DIM}. The thesis concludes with a set of policies and principles to apply to the
problem in light of valid arguments and threats.

### 2020-10-25 Thesis-Chapter2-Background.tex
Termify argument maps and remove strategy notes

The problem of strong encryption and \acl{EA} exists in a technical, historical, and regulatory context. This chapter
introduces cryptography, summarizes the history of encryption and the ``crypto wars,'' lists relevant encryption
regulations, and lists prominent technical \ac{EA} proposals. It then introduces argument maps as a logical modeling
tool, and introduces threat modeling with data flow diagrams.

@@

The arguments used in the \ac{EA} debate are diverse and complex; in order to advance the \ac{EA} discussion, it would
help to organize all the arguments used in a cohesive manner. One way to organize arguments is to create argument maps.
Argument maps are graphical representations of the logical structures and relationships between statements, premises,
and conclusions. Argument maps are an outgrowth of the same research by Horst Rittel that originated the idea of
\acp{wicked-prob}. In 1970 his research group developed \acp{IBIS} to break down \acp{wicked-prob} and document the
reasoned approaches that go into solving them \cite{kunz_issues_1970}. Interest in \ac{IBIS} has waxed and waned. Some
software tools have been developed, including the now-defunct gIBIS \cite{conklin_gibis_1988} and Compendium
\cite{dutoit_hypermedia_2006} tools designed to produce graphical representations. Argdown is a recent tool that
generates argument maps from structures specified in a Markdown-based language \cite{voigt_argdown_2018}.

>>>>

The problem of strong encryption and \acl{EA} exists in a technical, historical, and regulatory context. This chapter
introduces cryptography, summarizes the history of encryption and the ``crypto wars,'' lists relevant encryption
regulations, and lists prominent technical \ac{EA} proposals. It then introduces \acp{argmap} as a logical modeling
tool, and introduces threat modeling with data flow diagrams.

@@

The arguments used in the \ac{EA} debate are diverse and complex; in order to advance the \ac{EA} discussion, it would
help to organize all the arguments used in a cohesive manner. One way to organize arguments is to create \acp{argmap}.
\Acp{argmap} are graphical representations of the logical structures and relationships between statements, premises, and
conclusions. \Acp{argmap} are an outgrowth of the same research by Horst Rittel that originated the idea of
\acp{wicked-prob}. In 1970 his research group developed \acp{IBIS} to break down \acp{wicked-prob} and document the
reasoned approaches that go into solving them \cite{kunz_issues_1970}. Interest in \ac{IBIS} has waxed and waned. Some
software tools have been developed, including the now-defunct gIBIS \cite{conklin_gibis_1988} and Compendium
\cite{dutoit_hypermedia_2006} tools designed to produce graphical representations. Argdown is a recent tool that
generates \acp{argmap} from structures specified in a Markdown-based language \cite{voigt_argdown_2018}.
